---
name: Deon
surname: Roos
position: "Senior Statistical Ecologist"
address: "Animal and Plant Health Agency, York"
phone: +44 7872 329 714
email: "deonroos99@hotmail.com"
twitter: DeonRoos88
github: Deon88
orcid: 0000-0003-4866-7472
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am a quantitative ecologist specialising in population dynamics but have worked on questions varying from movement ecology to remote sensing in marine environments. I code predominantly in R (with extensions to `stan`, `JAGs`, and to a limited extent `INLA` [or `inlabru`]) and have developed a number of shiny apps (ranging from simulating data [e.g. occupancy modelling data] to internal data input and processing apps). I have experience both in empirical research and in developing individual-based-models. I am particularly keen on data visulation and the science that underlays effective visual communication.\nI speak English and Afrikaans fluently and can have basic conversions in Spanish (Castillian)."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Ecology (Population dynamics of a rodent crop pest)", "2016-2021", "University of Aberdeen", "Aberdeen, Scotland",
  "BSc Frist Class in Zoology", "2012-2016", "University of Aberdeen", "Aberdeen, Scotland"
) %>% 
  detailed_entries(
    Degree, 
    Year, 
    Institution, 
    Where)
```

# Employment

```{r}
tribble(
  ~Year, ~Job, ~Loc, ~Desc,
  
  "2021-22", 
  "Senior Statistical Ecologist", 
  "Animal and Plant Health Agency", 
  "Responsible for the statistical analysis for the wildlife department, including human mediated impacts on animal behaviour, abundance estimation, survival analysis (multi-state models).",
  
  "2021", 
  "Research Fellow", 
  "University of Aberdeen", 
  "Responsible for statistical analysis of various invasive species in Latin America, including unmarked abundance estimation and individual based models of INNS.",
  
  "2020-21", 
  "Teaching Fellow", 
  "University of Aberdeen", 
  "Course coordinator on Honour's population modelling course teaching abundance (DS, CMR), survival (CJS) and occupancy estimation and combining those estimates to predicty future trends using matrix models.",
  
  "2008-2012", 
  "Operating Department Support Worker", 
  "NHS Grampian", 
  "Non-sterile assistant in surgeries") |> 
  brief_entries(
    what = Loc,
    when = Year,
    with = Job,
    where = Desc,
    .protect = TRUE
  )
```

# Awards & prizes

Best Student Presentation, University of Aberdeen; "Treavelling waves as a form of spatio-temporal asynchrony".

Best Presentation, Iberian Vole Workshop; "Spatio temporal asynchrony in a cyclic vole species".

Sir Maitland Mackie Scholarship. Awarded funds for research activities in agricultural setting.

Zoology Award, University of Aberdeen. Awarded to outstanding Zoology students.

People's Trust for Endangered Species Summer Internship. Awarded funds to carry out additional research following BSc thesis.

Carnegie Summer Scholarship. Awarded funds to carry out data collection as part of BSc thesis.

# Publications

1. [__Roos D__](https://doi.org/10.1111/ele.14074), Caminero‐Saldaña C, Elston D, Mougeot F, García‐Ariza MC, Arroyo B, Luque-Larena JJ, Rojo-Revilla FJ, Lambin X (2022). From pattern to process? Dual travelling waves, with contrasting propagation speeds, best describe a self‐organised spatio‐temporal pattern in population growth of a cyclic rodents. Ecology Letters, 25(9): 1986-1998

2. [Slingsby J](https://doi.org/10.3390/jmse9050484), Scott BE, Kregting L, McIlvenny, Wilson J, Couto A, __Roos D__, Yanez M, Williamson BJ (2021). Surface Characterisation of Kolk-Boils within Tidal Stream Environments Using UAV Imagery. Journal of Marine Science and Engineering, 9(5): 484

3. [__Roos D__](https://doi.org/10.1016/j.agee.2018.11.013), Caminero‐Saldaña C, Arroyo B, Mougeot F, Luque-Larena JJ, Lambin X (2019). Unintentional effects of environmentally-friendly farming practices: Arising conflicts between zero-tillage and a crop pest, the common vole (Microtus arvalis). Agriculture, Ecosystems & Environment, 272:105-113

4. Douglas D, __Roos D__, Couto A, Mancini F, Lusseau D (2020). [Intro2R](https://intro2r.com/)

# References

Available upon request.
